### 2021-04-21 latex/article/article.tex
update

\bibliographystyle{elsarticle-num}
\bibliography{article}
\end{document}

>>>>

For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construnt the joint $\chi^2$ as 
\begin{align}
    \chi^2_{joint} = \chi^2_{IC} + \chi^2_{DC} + \chi^2_{P} - \chi^2_{IC,min} + \chi^2_{DC,min} + \chi^2_{P,min}\,
\end{align}
with test statistic $\chi^2_{joint,min}$.

\begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
       \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
       Cascade-like events
    \end{center}
    \caption{Ratio of detector level NSI to SI $\nu_\mu + \bar\nu_\mu$ fluxes. Dotted (dashed) lines show the region in which 90\% of the 
    DeepCore/PINGU (IceCube) data are contained}\label{fig:flux_ratio}
 \end{figure}
\bibliographystyle{elsarticle-num}
\bibliography{article}
\end{document}
